Make any stupid plot you want

### 2020-12-16 draft/sections/math.tex
germs

\begin{multline}
\tau(k) =(k, (r: \textrm{Temp}\rightarrow temp, r: \textrm{Time}\rightarrow time))\\
temp \in [temp_{min}, temp_{max}], time \in [time_{min}, time_{max}])
\end{multline}

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset K$ around every $k$. The inclusion map $\iota: U \rightarrow K$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

which through $\iota$ gets the data in $E$ at and near to $k$.

@@

>>>>

@@

\begin{align}
\tau(k) =(k, (r: \textrm{Temp}\rightarrow &temp, r: \textrm{Time}\rightarrow time))\\
&temp \in [temp_{min}, temp_{max}], time \in [time_{min}, time_{max}])
\end{align}

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset K$ around every $k$. The inclusion map $\iota: U \rightarrow K$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \begin{tikzcd}
        \xi^*E \arrow[d, "\pi" description]              & E \arrow[d, "\pi" description] \arrow[l, "\xi^*" description]            \\
        U \arrow[u, "\xi^*\tau" description, bend right] & K \arrow[u, "\tau" description, bend right] \arrow[l, "\xi" description]
    \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ $\xi^*\tau$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

which through $\iota$ gets the data in $E$ at and near to $k$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations.
